\LARGE \bf Human Tracking and Following in Dynamic Environment for Service Robots

### 2017-09-26 ieee-pandoc-template/paper_tencon2017.tex
added WC for prest at TENCON, and fix pdfExpress compatibility (no links or bookmarks allowed)

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Human Tracking and Following in Dynamic Environment for Service Robots},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[numbers,square]{natbib}
\bibliographystyle{IEEEtranN}

@@

\author{
	\IEEEauthorblockN{
		Adiwahono, A. H.\IEEEauthorrefmark{1}, 
		Saputra, V. B.\IEEEauthorrefmark{2}, 
		Ng, K. P.\IEEEauthorrefmark{5}, 
		Ren, Q.\IEEEauthorrefmark{6}, 
		Tan, B. H.\IEEEauthorrefmark{4}, 
		Chang, T.W.\IEEEauthorrefmark{3} 
		}
	\IEEEauthorblockA{%
		Institute for Infocomm Research \\
		1 Fusionopolis Way, Singapore 138632 \\
		Email: (\IEEEauthorrefmark{1}adiwahonoah  \IEEEauthorrefmark{2}saputravb  \IEEEauthorrefmark{5}ngkp  \IEEEauthorrefmark{6}renqy  \IEEEauthorrefmark{4}tanbh  \IEEEauthorrefmark{3}changtw  ) @i2r.a-star.edu.sg
	}
}

>>>>

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=false,
            pdfauthor={},
            pdftitle={Human Tracking and Following in Dynamic Environment for Service Robots},
            colorlinks=false,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[numbers,square]{natbib}
\bibliographystyle{IEEEtranN}

@@

\author{
	\IEEEauthorblockN{
		Adiwahono, A. H.\IEEEauthorrefmark{1}, 
		Saputra, V. B.\IEEEauthorrefmark{2}, 
		Ng, K. P.\IEEEauthorrefmark{5}, 
		Gao, W.\IEEEauthorrefmark{7}, 
		Ren, Q.\IEEEauthorrefmark{6}, 
		Tan, B. H.\IEEEauthorrefmark{4}, 
		Chang, T.W.\IEEEauthorrefmark{3} 
		}
	\IEEEauthorblockA{%
		Institute for Infocomm Research \\
		1 Fusionopolis Way, Singapore 138632 \\
		Email: (\IEEEauthorrefmark{1}adiwahonoah  \IEEEauthorrefmark{2}saputravb  \IEEEauthorrefmark{5}ngkp  \IEEEauthorrefmark{7}gaowc  \IEEEauthorrefmark{6}renqy  \IEEEauthorrefmark{4}tanbh  \IEEEauthorrefmark{3}changtw  ) @i2r.a-star.edu.sg
	}
}
